---
title: "CuvierModelSelection"
author: "RC + LB"
date: '2022-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
source("getPvalues.R")

data = data.frame(read.csv('E:/ModelingCovarData/Master_DFs/Cuvier_masterDF.csv'))
lagID = 41 
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# convert hours of presence back to # 5-min bins, then round to get Poisson dist
data$Pres = round(data$Pres*12)
```

# Test temperature at several time lags

```{r temp0Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp100Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp100")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp200Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp200")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp300Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp300")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp400Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp400")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp500Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp500")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp600Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp600")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r temp700Lags}

colInd = which(!is.na(str_match(colnames(data),"Temp700")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


# Test salinity at different time lags

```{r salinity0Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity100Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal100")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity200Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal200")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity300Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal300")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity400Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal400")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity500Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal500")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity600Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal600")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r salinity700Lags}

colInd = which(!is.na(str_match(colnames(data),"Sal700")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


# Test velocity magnitude at different depths
```{r velMag0Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag100Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag100")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag200Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag200")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag300Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag300")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag400Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag400")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag500Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag500")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag600Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag600")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velMag700Lags}

colInd = which(!is.na(str_match(colnames(data),"VelMag700")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```



# Test velocity aspect at different depths
```{r velAsp0Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp100Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp100")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp200Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp200")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp300Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp300")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp400Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp400")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp500Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp500")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp600Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp600")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


```{r velAsp700Lags}

colInd = which(!is.na(str_match(colnames(data),"VelAsp700")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


# Try SSH at 0m
```{r SSH0Lags}

colInd = which(!is.na(str_match(colnames(data),"SSH0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```




# Try Chl at 0m
```{r Chl0Lags}

colInd = which(!is.na(str_match(colnames(data),"Chl0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```



# Try FSLE at 0m
```{r FSLE0Lags}

colInd = which(!is.na(str_match(colnames(data),"FSLE0")))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

# AIC_comp = cbind(AIC(Lag0)[[1]],AIC(Lag7)[[1]],AIC(Lag14)[[1]],AIC(Lag21)[[1]],AIC(Lag28)[[1]],AIC(Lag42)[[1]],AIC(Lag56)[[1]])
# colnames(AIC_comp) = c("Lag0","Lag7","Lag14","Lag21","Lag28","Lag42","Lag56")
colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


Try GSLat at 0m
```{r GSLatLags}
# Test GSLat at several time lags
var = "GSLat"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```


Covar selection to start: Temp0Lag0
                          Temp700Lag42
                          Sal0Lag56
                          Sal700Lag42
                          VelMag0Lag42 
                          VelMag700mLag42
                          VelAsp0mLag0
                          VelAsp700mLag56
                          SSH0Lag28
                          Chl0Lag14
                          FSLE0Lag56
                          GSLatLag7
                          GSDist
                          Slope
                          Aspect
                          VelAsp700Lag56:Aspect


## THE FOLLOWING IS COPIED AND PASTED FROM BLAINVILLE'S, MODIFY FOR CUVIER'S BEFORE RUNNING

```{r checkVIF}
# calculate VIF for each of the variables desired in the full model
colMod = glm(Pres~Temp0Lag42
             +Temp700Lag7
             +Sal0Lag21
             # +Sal700Lag7
             +VelMag0Lag28 
             +VelMag700Lag7
             +VelAsp0Lag14 
             +VelAsp700Lag28
             +SSH0
             +Chl0Lag7
             +FSLE0
             +GSLatLag14
             +GSDist
             +Slope
             +Aspect,
             family=poisson,
             data=data)

VIFvals = vif(colMod)
VIFvals
# remove vars in stepwise fashion as necessary
```
Removing Salinity at 700m bc. highly collinear w Temp at 700m

```{r smooth vs linear}

# Test whether continuous covars should be included in model as linear or smooth terms
# (not testing Slope or Aspect as smooths...for now)

startTime = Sys.time()
smoothVarList = c("Temp0Lag42",
             "Temp700Lag7",
             "Sal0Lag21",
             "VelMag0Lag28" ,
             "VelMag700Lag7",
             "VelAsp0Lag14" ,
             "VelAsp700Lag28",
             "SSH0",
             "Chl0Lag7",
             "FSLE0",
             "GSLatLag14",
             "GSDist",
             "Slope",
             "Aspect")

termVote = matrix(ncol=length(smoothVarList),nrow=1)

for (i in 1:length(smoothVarList)){
  
  eval(parse(text=paste('linMod = geeglm(Pres~',smoothVarList[i],',family=poisson,data=data,id=GroupID,corstr=\"ar1\")',sep="")))
  
  eval(parse(text=paste('smoothMod=geeglm(Pres~mSpline(',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',prob=c(0.275,0.5,0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),family=poisson,data=data,id=GroupID,corstr=\"ar1\")',sep="")))
  
  QIC_vals = c(QIC(linMod)[[1]],QIC(smoothMod)[[1]])
  colnames(QIC_vals) = c("linMod","smoothMod")
  
  termVote[1,i] = colnames(QIC_vals)[which.min(QIC_vals)]
}

endTime = Sys.time()
endTime-startTime


```


```{r fullModel}
# Run full model and check autocorrelation of residuals, revise grouping variable if necessary

smoothVarList = c("Temp0Lag42",
             "Temp700Lag7",
             "Sal0Lag21",
             "VelMag0Lag28" ,
             "VelMag700Lag7",
             "VelAsp0Lag14" ,
             "VelAsp700Lag28",
             "SSH0",
             "Chl0Lag7",
             "FSLE0",
             "GSLatLag14",
             "GSDist",
             "Slope",
             "Aspect")

smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVararList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275, 0.5, 0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
 thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),sep=""))

colMod = geeglm(thisForm,
             family=poisson,
             data=data,
             id=GroupID,
            corstr="ar1")

modACF = acf(residuals(colMod),lag.max=180)

```


Changing the grouping variable doesn't have any effect at all on the residual autocorrelation, which is already quite minimal. Going with the most conservative grouping variable of 126 days.

```{r checkPV}
 #Add interaction term and run full model
thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),'+S_VelAsp700Lag28:Aspect',sep=""))

fullMod = geeglm(thisForm,
             family=poisson,
             data=data,
             id=GroupID,
            corstr="independence")

# Get p-values
getPvalues(fullMod)


```







