---
title: "CuvierModelSelection"
author: "RC + LB"
date: '2022-04-20'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
library(ggplot2)
library(gridExtra)
library(zoo)
library(pracma)
library(mgcv)
source("getPvalues.R")

data = data.frame(read.csv('J:/Chpt_3/ModelData/Cuvier_masterDF.csv'))
lagID = 41 
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# Round presence to get Poisson dist
data$Pres = round(data$Pres)
```

# Plot covar and presence time series to identify trends
```{r plot pres vs covars, fig.width=15, fig.height=10}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
covarList = c("Chl0",
              "SSH0",
              "FSLE0",
              "GSLat",
              "GSDist")

profileDir = 'J:/Chpt_3/CovarTS'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = unique(data$Site)

for (j in 1:length(sites)){
  
  plotList = list()
  plotDF = data.frame()
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  if (sum(data$Pres[siteInd]>0)>7){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=7,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=7,fill=NA),origin="1970-01-01"))
    
    plotList[['Pres']] = ggplot(plotDF,aes(x=Date)
    )+geom_line(aes(y=Pres)
    )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
    )+ggtitle('Presence'
    )+labs(x=NULL,y=NULL
    )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
    
    for (i in 1:length(covarList)){ # plot surface covars
      
      plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=7,fill=NA)
      plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
      )+geom_line(aes(y=Covar)
      )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
      )+coord_cartesian(xlim=c(startDate,endDate)
      )+ggtitle(covarList[i]
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
    }
    
    for (i in 1:length(profileList)){ # plot profiles of covars with multiple depth layers
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z)
      )+geom_contour_filled(
      )+coord_cartesian(xlim=c(startDate,endDate)
      )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
      )+scale_y_reverse(
      )+ggtitle(profileName
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
              legend.position="right",
              legend.title=element_text(size=0),
              legend.text=element_text(size=5),
              legend.key.size=unit(0.3,'lines'),
              legend.direction="vertical",
              legend.margin=margin(0))
      
    }
    
    grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+length(profileList)+1,top=paste('Cuvier at',sites[j]))
    
  }
}



```

# Plot pres vs. covars by year
```{r plot by year, fig.width=15, fig.height=8}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
dateMarks = c(seq.Date(startDate,endDate,by="year"),endDate)
covarList = c("Chl0",
              "SSH0",
              "FSLE0")

profileDir = 'J:/Chpt_3/CovarTS'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = c("HZ","WC","HAT")

for (j in 1:length(sites)){
  
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  
  if (sum(data$Pres[siteInd]>0)>50){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=3,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=3,fill=NA),origin="1970-01-01"))
    
    for (m in 1:(length(dateMarks)-1)){ # for each year
      
      plotList = list()
      st = dateMarks[m]
      ed = dateMarks[m+1]
      
      plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
      )+geom_line(aes(y=Pres)
      )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
      )+coord_cartesian(xlim=c(st,ed)
      )+ggtitle('Presence'
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      
      for (i in 1:length(covarList)){ # plot surface covars in this year
        
        plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=3,fill=NA)
        
        plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
        )+geom_line(aes(y=Covar)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle(covarList[i]
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      }
      
      grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+1,top=paste('Cuvier at',sites[j]))
      
    }
    
    
    for (i in 1:length(profileList)){ # for profiles of covars with multiple depth layers
      
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      for (m in 1:(length(dateMarks)-1)){
        st = dateMarks[m]
        ed = dateMarks[m+1]
        
        if (str_detect(profileName,"Asp")){
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          direction_labeller <- function(x){
            ifelse(x %% 45 == 0, c('E','NE','N','NW','W','SW','S','SE')[1+(as.integer(x/45) %% 8)], '')}
          my_colors=c("#2E22EA","#9E3DFB","#F86BE2","#FCCE7B","#C4E416","#4BBA0F","#447D87","#2C24E9")
          
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+scale_fill_manual(
            values=my_colors,
            guide=NULL
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          hues_df = data.frame(degree = 0:359) %>%
            mutate(
              label=direction_labeller(degree+90 %% 360),
              colors = colorRampPalette(my_colors)(360))
          
          plotList[["ColorLegend"]] = ggplot(hues_df
            )+geom_rect(aes(ymin=3,
                            ymax=4,
                            xmin=degree-0.5,
                            xmax=degree+0.5,
                            color=colors,
                            fill=colors)
            )+coord_polar(direction=-1,
                          start=0
            )+scale_color_identity(
            )+scale_fill_identity(
            )+guides(fill=FALSE,color=FALSE
            )+theme_void(
            )+ylim(c(1,4.5)
            )+geom_text(aes(x=degree,
                            y=4.5,
                            label=label)) 
          
          grid.arrange(plotList$Pres,plotList[[profileName]],plotList[["ColorLegend"]],
                       ncol=12,nrow=3,top=paste('Cuvier at',sites[j]),layout_matrix=rbind(c(rep(1,11),NA),
                                                                                          c(rep(2,11),NA),
                                                                                          c(rep(2,11),3)))
          
        } else {
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,40,0,0),unit="pt"))
                  
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
                  legend.position="right",
                  legend.title=element_text(size=0),
                  legend.text=element_text(size=7),
                  legend.key.size=unit(0.5,'lines'),
                  legend.direction="vertical",
                  legend.margin=margin(0))
          
          grid.arrange(plotList$Pres,plotList[[profileName]],
                       ncol=12,nrow=3,top=paste('Cuvier at',sites[j]),layout_matrix=rbind(c(rep(1,12)),
                                                                                          c(rep(2,12)),
                                                                                          c(rep(2,12))))
        }
      }
    }
  }
}

```

## Covar selection to start:
At WC presence peaks kind of correspond to high surface salinity, lower surface temp, 

Covar selection to start: Sal0
                          Temp0
                          Slope
                          Aspect




# Plot scatterplots and histograms
```{r plotCovars}
# Fill in smoothVarList based on selection made above
smoothVarList = c("SSH0",
                  "FSLE0",
                  "Sal0",
                  "Temp0",
                  "Temp700",
                  "VelMag700",
                  "VelAsp700",
                  "Sal700",
                  "GSLat",
                  "GSDist",
                  "Slope",
                  "Aspect")

pres = which(data$Pres>0)
presDF = data[pres,]
sites = unique(data$Site)

for (i in 1:length(smoothVarList)){
  
  # Plot presence bins across all data versus this covar
  edges = seq(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]),length.out=50)
  binDiff = diff(edges[1:2])
  plotDF = data.frame(Obs=histc(data[[smoothVarList[i]]],edges=edges)$cnt/dim(data)[1],
                      Pres=histc(presDF[[smoothVarList[i]]],edges=edges)$cnt/dim(presDF)[1],
                      BinCenter=seq(min(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    max(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    by=binDiff))
  
  print(ggplot(plotDF
  )+geom_col(aes(x=BinCenter,y=Obs),
             fill='#bfbfbf',
             alpha=0.6
  )+geom_col(aes(x=BinCenter,y=Pres),
             fill='#66B2FF',
             alpha=0.5
  ) + labs(y="Normalized Counts",x=NULL,title=smoothVarList[i]
  ) + theme_minimal())
  
  # print(ggplot(data
  # )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
  # )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
  #               method="loess"
  # )+labs(title=smoothVarList[i]))
  
  
  # Plot presence bins at each site versus this covar
  for (j in 1:length(sites)){
    siteInd = which(!is.na(str_match(data$Site,sites[j])))
    if (length(siteInd)>7){
      print(ggplot(data[siteInd,]
      )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
      )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
                    method="loess"
      )+labs(title=paste(smoothVarList[i],'at',sites[j])))
    }
  }
  
}

```


# Check VIF values
```{r checkVIF}
# calculate VIF for each of the variables desired in the full model
colMod = glm(Pres~Sal0
             +Temp0
             +Sal700
             +GSLat
             # +GSDist
             +Slope
             +Aspect
             +VelAsp700:Aspect,
             family=poisson,
             data=data)

VIFvals = vif(colMod)
VIFvals
# remove vars in stepwise fashion as necessary
```


Removing GSDist bc collinear w Aspect

# Test whether continuous covars should be included in model as linear or smooth terms

```{r smooth vs linear}

startTime = Sys.time()
smoothVarList = c("Temp0",
                  "Sal700",
                  "Sal0",
                  "VelAsp700",
                  "GSLat",
                  "Slope",
                  "Aspect")

modOpts = c("linMod","smoothMod")
AIC_votes = matrix(nrow=length(smoothVarList),ncol=3)

for (i in 1:length(smoothVarList)){
  
  # linMod = geeglm(Pres~data[[smoothVarList[i]]],data=data,family=poisson,id=GroupID,corstr="ar1")
  # 
  # smoothMod = geeglm(Pres~mSpline(data[[smoothVarList[i]]],
  #                                 knots=quantile(data[[smoothVarList[i]]],probs=c(0.275,0.5,0.725)),
  #                                 Boundary.knots=c(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]))),
  #                    data=data,
  #                    family=poisson,
  #                    id=GroupID,
  #                    corstr="ar1")
  
  modelCall = paste('gam(Pres~data$',smoothVarList[i],',data=data,family=poisson)',sep="")
  # modelCall = paste('geeglm(Pres~data$',smoothVarList[i],',data=data,family=poisson,id=GroupID,corstr="ar1")',sep="")
  linMod = eval(parse(text=modelCall))
  
  modelCall = paste('gam(Pres~s(data$',smoothVarList[i],',bs="cr"),data=data,family=poisson)',sep="")
  # modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275,0.5,0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod = eval(parse(text=modelCall))
  
  AIC_votes[i,1:2] = c(AIC(linMod)[[1]],AIC(smoothMod)[[1]])
  AIC_votes[i,3] = modOpts[which.min(AIC_votes[i,1:2])]
}

endTime = Sys.time()
endTime-startTime
colnames(AIC_votes) = c(modOpts,"Best")
rownames(AIC_votes) = smoothVarList
AIC_votes

```


```{r fullModel}
# Run full model and check autocorrelation of residuals, revise grouping variable if necessary

smoothVarList = c("Temp0",
                  "Sal700",
                  "Sal0",
                  "VelAsp700",
                  "GSLat",
                  "Slope",
                  "Aspect")

smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  if (str_detect(smoothVarList[i],"Asp")){
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275, 0.5, 0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')),periodic=TRUE)',sep="")))
  } else {
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275, 0.5, 0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  }
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),sep=""))

colMod = geeglm(thisForm,
                family=poisson,
                data=data,
                id=GroupID,
                corstr="ar1")

modACF = acf(residuals(colMod),lag.max=180)

```


Changing the grouping variable doesn't have any effect at all on the residual autocorrelation, which is already quite minimal. Going with the most conservative grouping variable of 126 days.


```{r checkPV}
#Add interaction term and run full model
thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),'+S_VelAsp700:Aspect',sep=""))

fullMod = geeglm(thisForm,
                 family=poisson,
                 data=data,
                 id=GroupID,
                 corstr="independence")

# Get p-values
getPvalues(fullMod)


```

