---
title: "KogiaModelSelection"
author: "RC + LB"
date: "4/22/2022"
output: html_document
---

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
library(ggplot2)
library(gridExtra)
library(zoo)
library(pracma)
library(mgcv)
library(SimDesign)
source("getPvalues.R")

data = data.frame(read.csv('J:/Chpt_3/ModelData/Kogia_masterDF.csv'))
lagID = 75
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# Round presence to get Poisson dist
data$Pres = round(data$Pres)
```

# Plot pres vs. covars by year
```{r plot by year, fig.width=15, fig.height=10}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
dateMarks = c(seq.Date(startDate,endDate,by="year"),endDate)
covarList = c("Chl0",
              "SSH0",
              "FSLE0")

profileDir = 'J:/Chpt_3/CovarTS'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = c("GS","BP","BS")
k=7

for (j in 1:length(sites)){
  
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  
  if (sum(data$Pres[siteInd]>0)>50){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=k,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=k,fill=NA),origin="1970-01-01"))
    
    for (m in 1:(length(dateMarks)-1)){ # for each year
      
      plotList = list()
      st = dateMarks[m]
      ed = dateMarks[m+1]
      
      plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
      )+geom_line(aes(y=Pres)
      )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
      )+coord_cartesian(xlim=c(st,ed)
      )+ggtitle('Presence'
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      
      for (i in 1:length(covarList)){ # plot surface covars in this year
        
        plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=k,fill=NA)
        
        plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
        )+geom_line(aes(y=Covar)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle(covarList[i]
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      }
      
      grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+1,top=paste('Kogia at',sites[j]))
      
    }
    
    
    for (i in 1:length(profileList)){ # for profiles of covars with multiple depth layers
      
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      for (m in 1:(length(dateMarks)-1)){
        st = dateMarks[m]
        ed = dateMarks[m+1]
        
        if (str_detect(profileName,"Asp")){
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          direction_labeller <- function(x){
            ifelse(x %% 45 == 0, c('E','NE','N','NW','W','SW','S','SE')[1+(as.integer(x/45) %% 8)], '')}
          my_colors=c("#2E22EA","#9E3DFB","#F86BE2","#FCCE7B","#C4E416","#4BBA0F","#447D87","#2C24E9")
          
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+scale_fill_manual(
            values=my_colors,
            guide=NULL
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          hues_df = data.frame(degree = 0:359) %>%
            mutate(
              label=direction_labeller(degree+90 %% 360),
              colors = colorRampPalette(my_colors)(360))
          
          plotList[["ColorLegend"]] = ggplot(hues_df
            )+geom_rect(aes(ymin=3,
                            ymax=4,
                            xmin=degree-0.5,
                            xmax=degree+0.5,
                            color=colors,
                            fill=colors)
            )+coord_polar(direction=-1,
                          start=0
            )+scale_color_identity(
            )+scale_fill_identity(
            )+guides(fill=FALSE,color=FALSE
            )+theme_void(
            )+ylim(c(1,4.5)
            )+geom_text(aes(x=degree,
                            y=4.5,
                            label=label)) 
          
          grid.arrange(plotList$Pres,plotList[[profileName]],plotList[["ColorLegend"]],
                       ncol=12,nrow=3,top=paste('Kogia at',sites[j]),layout_matrix=rbind(c(rep(1,11),NA),
                                                                                                   c(rep(2,11),NA),
                                                                                                   c(rep(2,11),3)))
          
        } else {
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,40,0,0),unit="pt"))
                  
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
                  legend.position="right",
                  legend.title=element_text(size=0),
                  legend.text=element_text(size=7),
                  legend.key.size=unit(0.5,'lines'),
                  legend.direction="vertical",
                  legend.margin=margin(0))
          

          grid.arrange(plotList$Pres,plotList[[profileName]],
                       ncol=12,nrow=3,top=paste('Kogia at',sites[j]),layout_matrix=rbind(c(rep(1,12)),
                                                                                                c(rep(2,12)),
                                                                                                c(rep(2,12))))
        }
      }
    }
  }
}


```

Covar selection to start: 
                  
# Plot scatterplots and histograms
```{r plotCovars}
# Fill in smoothVarList based on selection made above
smoothVarList = c("Temp0",
                  "Temp700",
                  "Sal0",
                  "Sal700",
                  "Chl0",
                  "SSH0",
                  "FSLE0",
                  "GSLat",
                  "Slope",
                  "Aspect")

pres = which(data$Pres>0)
presDF = data[pres,]
sites = c("GS","BP","BS")

for (i in 1:length(smoothVarList)){
  
  # Bootstrap the covar to produce a sample of the same size as pres
  refDist = sample(data[[smoothVarList[i]]],size=length(pres),replace=TRUE)
  
  # Compare empirical cumulative distribution functions with a Kolomogorov Smirnov test
  KS.out = ks.test(presDF[[smoothVarList[i]]],refDist,simulate.p.value=TRUE)
  
  # Plot presence bins across all data versus this covar
  edges = seq(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]),length.out=50)
  binDiff = diff(edges[1:2])
  plotDF = data.frame(Obs=histc(refDist,edges=edges)$cnt/length(refDist),
                      Pres=histc(presDF[[smoothVarList[i]]],edges=edges)$cnt/dim(presDF)[1],
                      BinCenter=seq(min(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    max(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    by=binDiff))
  
  print(ggplot(plotDF
  )+geom_col(aes(x=BinCenter,y=Obs),
             fill='#bfbfbf',
             alpha=0.6
  )+geom_col(aes(x=BinCenter,y=Pres),
             fill='#66B2FF',
             alpha=0.5
  ) + labs(y="Normalized Counts",
           x=NULL,
           title=paste(smoothVarList[i],', p = ',as.character(KS.out$p.value),sep="")
  ) + theme_minimal())
  
  # print(ggplot(data
  # )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
  # )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
  #               method="loess"
  # )+labs(title=smoothVarList[i]))
  
  # Plot presence bins at each site versus this covar
  if (!str_detect(smoothVarList[i],"Slope") & !str_detect(smoothVarList[i],"Aspect")){
    for (j in 1:length(sites)){
      siteInd = which(!is.na(str_match(data$Site,sites[j])))
      if (length(siteInd)>7){
        print(ggplot(data[siteInd,]
        )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
        )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
                      method="loess"
        )+labs(title=paste(smoothVarList[i],'at',sites[j])))
      }
    }
  }
}


```
                          
Full models will include: Temp0
                          Temp700
                          Sal0
                          Sal700
                          SSH0
                          Chl0
                          FSLE0
                          Slope
                          Aspect


# Test whether continuous covars should be included in model as linear or smooth terms
```{r smooth vs linear}

smoothVarList = c("Temp0",
                  "Temp700",
                  "Sal0",
                   "Sal700",
                   "SSH0",
                   "Chl0",
                  "FSLE0",
                  "GSDist",
                  "GSLat",
                  "Slope",
                   "Aspect")

startTime = Sys.time()

# modOpts = c("linMod","threeKnots","fourKnots","fiveKnots")
modOpts = c("linMod","threeKnots","fourKnots")
QIC_votes = matrix(nrow=length(smoothVarList),ncol=4)

# for (i in 1:(length(smoothVarList)-2)){
for (i in 1:7){

  # modelCall = paste('gam(Pres~data$',smoothVarList[i],',data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~data$',smoothVarList[i],',data=data,family=poisson,id=GroupID,corstr="ar1")',sep="")
  linMod = eval(parse(text=modelCall))
  
  # modelCall = paste('gam(Pres~s(data$',smoothVarList[i],',bs="cr"),data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.5)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod1 = eval(parse(text=modelCall))
  
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.333,0.666)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod2 = eval(parse(text=modelCall))
  
  # modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275,0.5,0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  # smoothMod3 = eval(parse(text=modelCall))
  
  QIC_votes[i,1:3] = c(QIC(linMod)[[1]],QIC(smoothMod1)[[1]],QIC(smoothMod2)[[1]])
  QIC_votes[i,4] = modOpts[which.min(QIC_votes[i,1:3])]
}

endTime = Sys.time()
endTime-startTime
colnames(QIC_votes) = c(modOpts,"Best")
rownames(QIC_votes) = smoothVarList[]
QIC_votes
```
        linMod             threeKnots         fourKnots          Best        
Temp0   "11814.1065545973" "11569.7340786689" "11463.1711103918" "fourKnots" 
Temp700 "10347.7532990548" "9580.20192404858" "9529.92030397718" "fourKnots" 
Sal0    "10496.2403672621" "10121.3570821702" "9994.25424985237" "fourKnots" 
Sal700  "10948.0927934031" "9711.88749289145" "9692.44497386357" "fourKnots" 
SSH0    "10173.0432411929" "9852.70858568363" "9767.00831446246" "fourKnots" 
Chl0    "10792.1204626858" "10433.8799469282" "10460.9388799915" "threeKnots"
FSLE0   "13358.8857649013" "13203.4124182884" "13207.3633288131" "threeKnots"
GSDist  "9914.87800494278" "9744.04358363257" "9757.6310364226"  "threeKnots"
GSLat   "13414.3643406766" "13406.651015688"  "13393.0233614703" "fourKnots" 
Slope   "11238.8226657821" "10495.3503766253" "10442.0107334561" "fourKnots" 
Aspect  NA                 NA                 NA                 NA          

# Make smooth terms, run full model and check collinearity
```{r fullModel}

smoothVarList = c("Temp0",
                  # "Temp700",
                  # "Sal0",
                   "Sal700",
                   "SSH0",
                   "Chl0",
                  "FSLE0",
                  # "GSDist",
                  "GSLat",
                  "Slope")
                   # "Aspect")
knotList = list(c(0.333,0.666),
                # c(0.333,0.666),
                # c(0.333,0.666),
                c(0.333,0.666),
                c(0.333,0.666),
                c(0.5),
                c(0.5),
                # c(0.5),
                c(0.333,0.666),
                c(0.333,0.666))
                # c(0.333,0.666))
linVarList = c()

smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  if (str_detect(smoothVarList[i],"Asp")){
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')),periodic=TRUE)',sep="")))
  } else {
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  }
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))

fullMod = geeglm(thisForm,
                family=poisson,
                data=data,
                id=GroupID,
                corstr="ar1")

VIFvals = vif(fullMod)
VIFvals = cbind(VIFvals,(VIFvals[,3])^2)
colnames(VIFvals)[4] = "LOOK AT ME"
VIFvals
# remove vars in stepwise fashion as necessary
```
Removing Sal0, Temp700, GSDist, Aspect

# Check autocorrelation of residuals, revise grouping variable if necessary
```{r}
modACF = acf(residuals(fullMod),lag.max=180)

```

#Check term significance
```{r fullMod}

if (fullMod$geese$error==1){
  print("Model did not converge")
} else {PV = getPvalues(fullMod)}


```
Variable    p-value
S_Temp0	    0.006013			
S_Sal700	  0.003949			
S_SSH0	    6e-04			
S_Chl0	    0.792672			
S_FSLE0	    0.079506			
S_GSLat	    0.078701			
S_Slope	    <0.0001

#Remove non-significant terms, re-run model, check p-values
```{r fullMod}

PV$'p-value'[PV$'p-value'=="<0.0001"] = 0.0001
badVars = PV$Variable[(as.numeric(PV$'p-value')>=0.05)]
redMod<-eval(parse(text=paste("update(fullMod, . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
if (redMod$geese$error==1){
  print("Model did not converge")
} else {PVred = getPvalues(redMod)
PVred$'p-value'[PVred$'p-value'=="<0.0001"] = 0.0001
PVred}

```
Variable    p-value
S_Temp0	    0.000469			
S_Sal700	  0.003288			
S_SSH0	    0.00034			
S_Slope	    1e-04

# Plot terms from regional model
```{r plot regional}
source("plotSmooths.R")
source("plotLinears.R")

smoothVarList = c("Temp0",
                   "Sal700",
                   "SSH0",
                  "Slope")
knotList = list(c(0.333,0.666),
                c(0.333,0.666),
                c(0.333,0.666),
                c(0.333,0.666))

terms = names(redMod$model)[2:length(names(redMod$model))]

for (i in 1:length(terms)){
  if (str_detect(terms[i],"S_")){ # plot smooth terms
    term = str_remove(terms[i],"S_")
    knotInd = which(!is.na(str_match(smoothVarList,term)))
    k=length(unlist(knotList[knotInd]))+2
  coefInd = which(str_detect(names(redMod$coefficients),term))
  if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
  print(plotSmooths(redMod,term,coefInd,k,periodic,site=NA,title=NULL))
  } else { # plot linear terms
  coefInd = which(str_detect(names(redMod$coefficients),terms[i]))
  print(plotLinears(redMod,term,coefInd,site=NA,title=NULL))
  }
}

```

# Create site-specific models
# Don't include slope or aspect because they're only a single value for each site
```{r site-specific models}

sites = c("GS","BP","BS")
smoothVarList = c("Temp0",
                   "Sal700",
                   "SSH0",
                   "Chl0",
                  "FSLE0",
                  "GSLat")
knotList = list(c(0.333,0.666),
                c(0.333,0.666),
                c(0.333,0.666),
                c(0.5),
                c(0.5),
                c(0.333,0.666))
linVarList = c()
siteModList = list()
pValList = list()


for (j in 1:length(sites)){
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  modDF = data[siteInd,]
  
  smoothNameList = character()
  
  for (i in 1:length(smoothVarList)){
    
    if (str_detect(smoothVarList[i],"Asp")){
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')),periodic=TRUE)',sep="")))
    } else {
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')))',sep="")))
    }
    
    smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
  }
  
  thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))
  
  siteModList[[sites[j]]] = geeglm(thisForm,
                                  family=poisson,
                                  data=modDF,
                                  id=GroupID,
                                  corstr="ar1")
  
  if (siteModList[[sites[j]]]$geese$error!=1){
  pValList[[sites[j]]] = getPvalues(siteModList[[sites[j]]])
  pValList[[sites[j]]]$'p-value'[pValList[[sites[j]]]$'p-value'=="<0.0001"] = 0.0001
  } else {pValList[[sites[j]]]="NC"}
  
}

print(pValList)

```

$GS
  Variable  p-value
1  S_Temp0    1e-04
2 S_Sal700 0.005644
3   S_SSH0 0.004435
4   S_Chl0 0.183797
5  S_FSLE0 0.016051
6  S_GSLat 0.000121

$BP
  Variable  p-value
1  S_Temp0    1e-04
2 S_Sal700 0.293957
3   S_SSH0    1e-04
4   S_Chl0    1e-04
5  S_FSLE0    1e-04
6  S_GSLat  0.26674

$BS
  Variable  p-value
1  S_Temp0 0.010911
2 S_Sal700 0.167473
3   S_SSH0 0.000151
4   S_Chl0    1e-04
5  S_FSLE0 0.006624
6  S_GSLat    1e-04

# Remove non-significant terms and rerun
```{r site-specific models}

siteModListRed = list()
pValListRed = list()
for (i in 1:length(siteModList)){
  site = names(siteModList)[i]
  if (is.list(pValList[[site]])){
  badVars = pValList[[site]]$Variable[as.numeric(pValList[[site]]$'p-value')>=0.05]
    if (!isempty(badVars)){
  siteModListRed[[site]]<-eval(parse(text=paste("update(siteModList[[site]], . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
   if (siteModListRed[[site]]$geese$error!=1){
  pValListRed[[site]] = getPvalues(siteModListRed[[site]])
  pValListRed[[site]]$'p-value'[pValListRed[[site]]$'p-value'=="<0.0001"] = 0.0001
  } else {pValListRed[[site]]="NC"}
    } else {
      siteModListRed[[site]] = siteModList[[site]]
      pValListRed[[site]] = pValList[[site]]
    }
  } else {
    siteModListRed[[site]] = list()
      pValListRed[[site]] = "NC"
  }
}

print(pValListRed)
```

$GS
  Variable  p-value
1  S_Temp0 0.038869
2 S_Sal700 0.183139
3   S_SSH0 0.002027
4  S_FSLE0 0.006213
5  S_GSLat 0.000235

$BP
  Variable  p-value
1  S_Temp0 0.000955
2   S_SSH0    1e-04
3   S_Chl0    1e-04
4  S_FSLE0  0.00222

$BS
  Variable  p-value
1  S_Temp0 0.001029
2   S_SSH0    1e-04
3   S_Chl0    1e-04
4  S_FSLE0 0.014178
5  S_GSLat 0.001373

# Again, remove non-significant terms and rerun
```{r site-specific models}

for (i in 1:length(siteModListRed)){
  site = names(siteModListRed)[i]
  if (is.list(pValListRed[[site]])){
  badVars = pValListRed[[site]]$Variable[as.numeric(pValListRed[[site]]$'p-value')>=0.05]
    if (!isempty(badVars)){
  siteModListRed[[site]]<-eval(parse(text=paste("update(siteModListRed[[site]], . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
   if (siteModListRed[[site]]$geese$error!=1){
  pValListRed[[site]] = getPvalues(siteModListRed[[site]])
  pValListRed[[site]]$'p-value'[pValListRed[[site]]$'p-value'=="<0.0001"] = 0.0001
  } else {pValListRed[[site]]="NC"}
    }
  } 
}

print(pValListRed)
```

# Plot terms from site-specific models
```{r plot sites specific models}

source("plotSmooths.R")
source("plotLinears.R")

smoothVarList = c("Temp0",
                   "Sal700",
                   "SSH0",
                   "Chl0",
                  "FSLE0",
                  "GSLat")
knotList = list(c(0.333,0.666),
                c(0.333,0.666),
                c(0.333,0.666),
                c(0.5),
                c(0.5),
                c(0.333,0.666))
linVarList = c()

for (j in 1:length(siteModListRed)){
  if (siteModListRed[[j]]$geese$error!=1){
    terms = names(siteModListRed[[j]]$model)[2:length(names(siteModListRed[[j]]$model))]
   
    siteName = names(siteModListRed)[j]
    
    for (i in 1:length(terms)){
      if (str_detect(terms[i],"S_")){ # plot smooth terms
        term = str_remove(terms[i],"S_")
         knotInd = which(!is.na(str_match(smoothVarList,term)))
        k=length(unlist(knotList[knotInd]))+2
        coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),term))
        if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
        print(plotSmooths(siteModListRed[[j]],term,coefInd,k,periodic,site=siteName,title=siteName))
      } else { # plot linear terms
        term=terms[i]
        coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),terms[i]))
        print(plotLinears(siteModListRed[[j]],term,coefInd,site=siteName,title=siteName))
      }
    }
  }
}

```