---
title: "RissoModelSelection"
author: "RC + LB"
date: "4/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
library(ggplot2)
library(gridExtra)
library(zoo)
library(pracma)
library(mgcv)
library(SimDesign)
source("getPvalues.R")

data = data.frame(read.csv('J:/Chpt_3/ModelData/Risso_masterDF.csv'))
lagID = 81
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# Round presence to get Poisson dist
data$Pres = round(data$Pres)
```

# Plot pres vs. covars by year
```{r plot by year, fig.width=15, fig.height=10}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
dateMarks = c(seq.Date(startDate,endDate,by="year"),endDate)
covarList = c("Chl0",
              "SSH0",
              "FSLE0")

profileDir = 'J:/Chpt_3/CovarTS'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = c("HZ","NC","NFC","GS")
k=14

for (j in 1:length(sites)){
  
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  
  if (sum(data$Pres[siteInd]>0)>50){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=k,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=k,fill=NA),origin="1970-01-01"))
    
    for (m in 1:(length(dateMarks)-1)){ # for each year
      
      plotList = list()
      st = dateMarks[m]
      ed = dateMarks[m+1]
      
      plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
      )+geom_line(aes(y=Pres)
      )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
      )+coord_cartesian(xlim=c(st,ed)
      )+ggtitle('Presence'
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      
      for (i in 1:length(covarList)){ # plot surface covars in this year
        
        plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=k,fill=NA)
        
        plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
        )+geom_line(aes(y=Covar)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle(covarList[i]
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      }
      
      grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+1,top=paste('Risso at',sites[j]))
      
    }
    
    
    for (i in 1:length(profileList)){ # for profiles of covars with multiple depth layers
      
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      for (m in 1:(length(dateMarks)-1)){
        st = dateMarks[m]
        ed = dateMarks[m+1]
        
        if (str_detect(profileName,"Asp")){
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          direction_labeller <- function(x){
            ifelse(x %% 45 == 0, c('E','NE','N','NW','W','SW','S','SE')[1+(as.integer(x/45) %% 8)], '')}
          my_colors=c("#2E22EA","#9E3DFB","#F86BE2","#FCCE7B","#C4E416","#4BBA0F","#447D87","#2C24E9")
          
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+scale_fill_manual(
            values=my_colors,
            guide=NULL
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          hues_df = data.frame(degree = 0:359) %>%
            mutate(
              label=direction_labeller(degree+90 %% 360),
              colors = colorRampPalette(my_colors)(360))
          
          plotList[["ColorLegend"]] = ggplot(hues_df
            )+geom_rect(aes(ymin=3,
                            ymax=4,
                            xmin=degree-0.5,
                            xmax=degree+0.5,
                            color=colors,
                            fill=colors)
            )+coord_polar(direction=-1,
                          start=0
            )+scale_color_identity(
            )+scale_fill_identity(
            )+guides(fill=FALSE,color=FALSE
            )+theme_void(
            )+ylim(c(1,4.5)
            )+geom_text(aes(x=degree,
                            y=4.5,
                            label=label)) 
          
          grid.arrange(plotList$Pres,plotList[[profileName]],plotList[["ColorLegend"]],
                       ncol=12,nrow=3,top=paste('Risso at',sites[j]),layout_matrix=rbind(c(rep(1,11),NA),
                                                                                                   c(rep(2,11),NA),
                                                                                                   c(rep(2,11),3)))
          
        } else {
          
        plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
        )+geom_line(aes(y=Pres)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle('Presence'
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,40,0,0),unit="pt"))
                  
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
                  legend.position="right",
                  legend.title=element_text(size=0),
                  legend.text=element_text(size=7),
                  legend.key.size=unit(0.5,'lines'),
                  legend.direction="vertical",
                  legend.margin=margin(0))
          

          grid.arrange(plotList$Pres,plotList[[profileName]],
                       ncol=12,nrow=3,top=paste('Risso at',sites[j]),layout_matrix=rbind(c(rep(1,12)),
                                                                                                c(rep(2,12)),
                                                                                                c(rep(2,12))))
        }
      }
    }
  }
}


```
HZ:
  High pres during high surface temps, somewhat during high surface sal, somewhat during high sal200
NC:
  2/3 years high pres during high surface temps
NFC:
  
GS:
  Kind of inverse w. SSH

Covar selection to start: Temp0
                          Sal0
                          Sal200
                          SSH0
                  
# Plot scatterplots and histograms
```{r plotCovars}
# Fill in smoothVarList based on selection made above
smoothVarList = c("Temp0",
                  "Sal0",
                  "Sal200",
                  "SSH0",
                  "FSLE0",
                  "GSLat",
                  "Slope",
                  "Aspect")

pres = which(data$Pres>0)
presDF = data[pres,]
sites = c("HZ","NC","NFC","GS")

for (i in 1:length(smoothVarList)){
  
  # Bootstrap the covar to produce a sample of the same size as pres
  refDist = sample(data[[smoothVarList[i]]],size=length(pres),replace=TRUE)
  
  # Compare empirical cumulative distribution functions with a Kolomogorov Smirnov test
  KS.out = ks.test(presDF[[smoothVarList[i]]],refDist,simulate.p.value=TRUE)
  
  # Plot presence bins across all data versus this covar
  edges = seq(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]),length.out=50)
  binDiff = diff(edges[1:2])
  plotDF = data.frame(Obs=histc(refDist,edges=edges)$cnt/length(refDist),
                      Pres=histc(presDF[[smoothVarList[i]]],edges=edges)$cnt/dim(presDF)[1],
                      BinCenter=seq(min(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    max(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    by=binDiff))
  
  print(ggplot(plotDF
  )+geom_col(aes(x=BinCenter,y=Obs),
             fill='#bfbfbf',
             alpha=0.6
  )+geom_col(aes(x=BinCenter,y=Pres),
             fill='#66B2FF',
             alpha=0.5
  ) + labs(y="Normalized Counts",
           x=NULL,
           title=paste(smoothVarList[i],', p = ',as.character(KS.out$p.value),sep="")
  ) + theme_minimal())
  
  # print(ggplot(data
  # )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
  # )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
  #               method="loess"
  # )+labs(title=smoothVarList[i]))
  
  # Plot presence bins at each site versus this covar
  if (!str_detect(smoothVarList[i],"Slope") & !str_detect(smoothVarList[i],"Aspect")){
    for (j in 1:length(sites)){
      siteInd = which(!is.na(str_match(data$Site,sites[j])))
      if (length(siteInd)>7){
        print(ggplot(data[siteInd,]
        )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
        )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
                      method="loess"
        )+labs(title=paste(smoothVarList[i],'at',sites[j])))
      }
    }
  }
}


```
                          
Full models will include: Temp0
                          Sal0
                          Sal200
                          SSH0
                          FSLE0
                          Slope
                          Aspect


# Test for how a term should be included in the model
```{r smooth vs linear}

# Test whether continuous covars should be included in model as linear or smooth terms

startTime = Sys.time()
smoothVarList = c("SSH0",
                    "Sal0",
                    "Sal200",
                    "Temp0",
                    "FSLE0",
                    "Slope",
                    "Aspect")

modOpts = c("linMod","threeKnots","fourKnots","fiveKnots")
QIC_votes = matrix(nrow=length(smoothVarList),ncol=5)

for (i in 1:(length(smoothVarList)-2)){

  # modelCall = paste('gam(Pres~data$',smoothVarList[i],',data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~data$',smoothVarList[i],',data=data,family=poisson,id=GroupID,corstr="ar1")',sep="")
  linMod = eval(parse(text=modelCall))
  
  # modelCall = paste('gam(Pres~s(data$',smoothVarList[i],',bs="cr"),data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.5)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod1 = eval(parse(text=modelCall))
  
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.333,0.666)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod2 = eval(parse(text=modelCall))
  
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275,0.5,0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod3 = eval(parse(text=modelCall))
  
  QIC_votes[i,1:4] = c(QIC(linMod)[[1]],QIC(smoothMod1)[[1]],QIC(smoothMod2)[[1]],QIC(smoothMod3)[[1]])
  QIC_votes[i,5] = modOpts[which.min(QIC_votes[i,1:4])]
}

endTime = Sys.time()
endTime-startTime
colnames(QIC_votes) = c(modOpts,"Best")
rownames(QIC_votes) = smoothVarList[]
QIC_votes
```
Can't do Temp0 linear, FSLE w 5 knots; no point in doing aspect w <4 (periodic)

              linMod            threeKnots             fourKnots           fiveKnots           Best        
SSH0   "-296735.177138483" "4.70302171768354e+94" "-305103.492705936" "-303855.841971739" "fourKnots" 
Sal0   "-268213.11632774"  "-290167.503400889"    "-293992.077502191" "-293195.86827238"  "fourKnots" 
Sal200 "-282030.687502245" "-289539.302321496"    "-289467.806522269" "-290222.87324893"  "fiveKnots" 
Temp0  NA                  "-274409.778665695"    "-273816.055322142" "-275248.862901652" "fiveKnots" 
FSLE0  "-269439.332599339" "-269449.916536072"    "-269263.488955822" NA                  "threeKnots"
Slope  "-269581.680037984" "-312071.374614257"    "-291594.730586389" "-291045.107182842" "threeKnots"
Aspect NA                  NA                     "-308558.801557419" "-309559.156012864" "fiveKnots" 

# Make smooth terms, run full model and check collinearity
```{r fullModel}

smoothVarList = c("SSH0",
                  "Sal0",
                  "Sal200",
                  "Temp0",
                  "FSLE0",
                  "Slope",
                  "Aspect")
knotList = list(c(0.333,0.666),
             c(0.333,0.666),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.333,0.666))
linVarList = c()

smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  if (str_detect(smoothVarList[i],"Asp")){
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')),periodic=TRUE)',sep="")))
  } else {
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  }
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))

fullMod = geeglm(thisForm,
                family=poisson,
                data=data,
                id=GroupID,
                corstr="ar1")

VIFvals = vif(fullMod)
VIFvals = cbind(VIFvals,(VIFvals[,3])^2)
colnames(VIFvals)[4] = "LOOK AT ME"
VIFvals
# remove vars in stepwise fashion as necessary
```
              GVIF Df GVIF^(1/(2*Df)) LOOK AT ME
S_SSH0   27.384364  5        1.392356   1.938655
S_Sal0   15.000441  5        1.311023   1.718782
S_Sal200 11.966679  4        1.363787   1.859916
S_Temp0   8.284181  4        1.302510   1.696533
S_FSLE0   6.204775  4        1.256292   1.578271
S_Slope  23.437862  4        1.483337   2.200288
S_Aspect  8.421711  2        1.703531   2.902018

Looks good!


# Check autocorrelation of residuals, revise grouping variable if necessary
```{r}
modACF = acf(residuals(fullMod),lag.max=180)

```

#Check term significance
```{r fullMod}

if (fullMod$geese$error==1){
  print("Model did not converge")
} else {PV = getPvalues(fullMod)}

```


#Remove non-significant terms, re-run model, check p-values
```{r redMod}

PV$'p-value'[PV$'p-value'=="<0.0001"] = 0.0001
badVars = PV$Variable[(PV$'p-value'>=0.05)]
redMod<-eval(parse(text=paste("update(fullMod, . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
if (redMod$geese$error==1){
  print("Model did not converge")
} else {PVred = getPvalues(redMod)
PVred$'p-value'[PVred$'p-value'=="<0.0001"] = 0.0001
PVred}


```


# Plot terms from regional model
```{r plot regional}
source("plotSmooths.R")
source("plotLinears.R")

smoothVarList = c("FSLE0",
                  "Slope")
knotList = list(c(0.5),
                c(0.5))
terms = names(redMod$model)[2:length(names(redMod$model))]


for (i in 1:length(terms)){
  if (str_detect(terms[i],"S_")){ # plot smooth terms
    term = str_remove(terms[i],"S_")
    knotInd = which(!is.na(str_match(smoothVarList,term)))
    k=length(unlist(knotList[knotInd]))+2
  coefInd = which(str_detect(names(redMod$coefficients),term))
  if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
  print(plotSmooths(redMod,term,coefInd,k,periodic,site=NA,title=NULL))
  } else { # plot linear terms
    term=terms[i]
  coefInd = which(str_detect(names(redMod$coefficients),terms))
  print(plotLinears(redMod,term,coefInd,site=NA,title=NULL))
  }
}

```

# Create site-specific models
# Don't include slope or aspect because they're only a single value for each site
```{r site-specific models}

sites = c("HZ","OC","NC","BC","NFC","HAT","GS")
smoothVarList = c("SSH0",
                  "Sal0",
                  "Sal200",
                  "Temp0",
                  "FSLE0")
knotList = list(c(0.333,0.666),
             c(0.333,0.666),
             c(0.5),
             c(0.5),
             c(0.5))
linVarList = c()
siteModList = list()
pValList = list()


for (j in 1:length(sites)){
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  modDF = data[siteInd,]
  
  smoothNameList = character()
  
  for (i in 1:length(smoothVarList)){
    
    if (str_detect(smoothVarList[i],"Asp")){
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')),periodic=TRUE)',sep="")))
    } else {
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')))',sep="")))
    }
    
    smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
  }
  
  thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))
  
  siteModList[[sites[j]]] = geeglm(thisForm,
                                  family=poisson,
                                  data=modDF,
                                  id=GroupID,
                                  corstr="ar1")
  
  if (siteModList[[sites[j]]]$geese$error!=1){
  pValList[[sites[j]]] = getPvalues(siteModList[[sites[j]]])
  pValList[[sites[j]]]$'p-value'[pValList[[sites[j]]]$'p-value'=="<0.0001"] = 0.0001
  } else {pValList[[sites[j]]]="NC"}
  
}

print(pValList)

```

$HZ
[1] "NC"

$OC
[1] "NC"

$NC
  Variable  p-value
1   S_SSH0 0.019411
2   S_Sal0 0.026113
3 S_Sal200  <0.0001
4  S_Temp0  <0.0001
5  S_FSLE0 0.013921

$BC
[1] "NC"

$NFC
[1] "NC"

$HAT
  Variable  p-value
1   S_SSH0 0.000276
2   S_Sal0  <0.0001
3 S_Sal200 0.000445
4  S_Temp0 0.011524
5  S_FSLE0  <0.0001

$GS
  Variable  p-value
1   S_SSH0 0.001943
2   S_Sal0 0.000877
3 S_Sal200  <0.0001
4  S_Temp0 0.850605
5  S_FSLE0 0.169599


# Remove non-significant terms and rerun
```{r site-specific models}

siteModListRed = list()
pValListRed = list()
for (i in 1:length(siteModList)){
  site = names(siteModList)[i]
  if (is.list(pValList[[site]])){
  badVars = pValList[[site]]$Variable[as.numeric(pValList[[site]]$'p-value')>=0.05]
    if (!isempty(badVars)){
  siteModListRed[[site]]<-eval(parse(text=paste("update(siteModList[[site]], . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
   if (siteModListRed[[site]]$geese$error!=1){
  pValListRed[[site]] = getPvalues(siteModListRed[[site]])
  pValListRed[[site]]$'p-value'[pValListRed[[site]]$'p-value'=="<0.0001"] = 0.0001
  } else {pValListRed[[site]]="NC"}
    } else {
      siteModListRed[[site]] = siteModList[[site]]
      pValListRed[[site]] = pValList[[site]]
    }
  } else {
    siteModListRed[[site]] = list()
      pValListRed[[site]] = "NC"
  }
}


print(pValListRed)
```
$HZ
[1] "NC"

$OC
[1] "NC"

$NC
  Variable  p-value
1   S_SSH0 0.019411
2   S_Sal0 0.026113
3 S_Sal200    1e-04
4  S_Temp0    1e-04
5  S_FSLE0 0.013921

$BC
[1] "NC"

$NFC
[1] "NC"

$HAT
  Variable  p-value
1   S_SSH0 0.000276
2   S_Sal0    1e-04
3 S_Sal200 0.000445
4  S_Temp0 0.011524
5  S_FSLE0    1e-04

$GS
  Variable  p-value
1   S_SSH0    1e-04
2   S_Sal0 0.049268
3 S_Sal200    1e-04


# Plot terms from site-specific models
```{r plot sites specific models}

source("plotSmooths.R")
source("plotLinears.R")

smoothVarList = c("SSH0",
                  "Sal0",
                  "Sal200",
                  "Temp0",
                  "FSLE0")
knotList = list(c(0.333,0.666),
             c(0.333,0.666),
             c(0.5),
             c(0.5),
             c(0.5))

for (j in 1:length(siteModListRed)){
  if (siteModListRed[[j]]$geese$error!=1){
    terms = names(siteModListRed[[j]]$model)[2:length(names(siteModListRed[[j]]$model))]
   
    siteName = names(siteModListRed)[j]
    
    for (i in 1:length(terms)){
      if (str_detect(terms[i],"S_")){ # plot smooth terms
        term = str_remove(terms[i],"S_")
         knotInd = which(!is.na(str_match(smoothVarList,term)))
        k=length(unlist(knotList[knotInd]))+2
        coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),term))
        if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
        print(plotSmooths(siteModListRed[[j]],term,coefInd,k,periodic,site=siteName,title=siteName))
      } else { # plot linear terms
        term=terms[i]
        coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),terms[i]))
        print(plotLinears(siteModListRed[[j]],term,coefInd,site=siteName,title=siteName))
      }
    }
  }
}

```

