---
title: "SBCD"
author: "RC + LB"
date: "4/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
library(ggplot2)
library(gridExtra)
library(zoo)
library(pracma)
library(mgcv)
library(SimDesign)
library(multitaper)
source("getPvalues.R")

data = data.frame(read.csv('E:/ModelingCovarData/Master_DFs/UD28_masterDF.csv'))
lagID = 126
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# Round presence to get Poisson dist
data$Pres = round(data$Pres)
```

# Plot covar and presence time series to identify trends
```{r plot pres vs covars, fig.width=15, fig.height=10}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
covarList = c("Chl0",
              "SSH0",
              "GSLat",
              "GSDist",
              "FSLE0")

profileDir = 'J:/Chpt_3/CovarTS'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = unique(data$Site)

for (j in 1:length(sites)){
  
  plotList = list()
  plotDF = data.frame()
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  if (sum(data$Pres[siteInd]>0)>7){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=7,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=7,fill=NA),origin="1970-01-01"))
    
    plotList[['Pres']] = ggplot(plotDF,aes(x=Date)
    )+geom_line(aes(y=Pres)
    )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
    )+ggtitle('Presence'
    )+labs(x=NULL,y=NULL
    )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
    
    for (i in 1:length(covarList)){ # plot surface covars
      
      plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=7,fill=NA)
      plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
      )+geom_line(aes(y=Covar)
      )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
      )+coord_cartesian(xlim=c(startDate,endDate)
      )+ggtitle(covarList[i]
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
    }
    
    for (i in 1:length(profileList)){ # plot profiles of covars with multiple depth layers
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z)
      )+geom_contour_filled(
      )+coord_cartesian(xlim=c(startDate,endDate)
      )+scale_x_continuous(breaks=c(seq.Date(from=startDate,to=endDate,by="quarter"))
      )+scale_y_reverse(
      )+ggtitle(profileName
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
              legend.position="right",
              legend.title=element_text(size=0),
              legend.text=element_text(size=5),
              legend.key.size=unit(0.3,'lines'),
              legend.direction="vertical",
              legend.margin=margin(0))
      
    }
    
    grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+length(profileList)+1,top=paste('Common Dolphins at',sites[j]))
    
  }
}



```




```{r}
site = "BC"
siteInd = which(!is.na(str_match(data$Site,site)))
thisTS = ts(data$Pres[siteInd],start=data$Date[siteInd[1]],end=data$Date[siteInd[length(siteInd)]],deltat=1/7)
spec.mtm(thisTS)

spectrum(data$Pres[siteInd])
spec.pgram(data$Pres[siteInd])
spec.ar(data$Pres[siteInd])
I <- abs(fft(data$Pres[siteInd]))^2/length(siteInd)
P <- (4/240)*I[1:120]
f <- 0:119/240
plot(f[-1],P[-1], type="l", xlab="Frequency", ylab="Power")
```

# Plot pres vs. covars by year
```{r plot by year, fig.width=15, fig.height=10}

startDate = as.Date("2016-05-01",origin="1970-01-01")
endDate = as.Date("2019-04-30",origin="1970-01-01")
dateMarks = c(seq.Date(startDate,endDate,by="year"),endDate)
covarList = c("Chl0",
              "SSH0",
              "FSLE0")

profileDir = 'E:/ModelingCovarData/Profiles'
profileList = dir(profileDir,pattern="Profiles_ES.Rdata",full.names=TRUE)
sites = c("HZ","OC","NC","BC","WC","NFC","HAT","GS","BP","BS")
k=7

for (j in 1:length(sites)){
  
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  
  
  if (sum(data$Pres[siteInd]>0)>50){
    
    plotDF = data.frame(Pres = rollmean(data$Pres[siteInd],k=k,fill=NA),
                        Date = as.Date(rollmean(data$Date[siteInd],k=k,fill=NA),origin="1970-01-01"))
    
    for (m in 1:(length(dateMarks)-1)){ # for each year
      
      plotList = list()
      st = dateMarks[m]
      ed = dateMarks[m+1]
      
      plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
      )+geom_line(aes(y=Pres)
      )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
      )+coord_cartesian(xlim=c(st,ed)
      )+ggtitle('Presence'
      )+labs(x=NULL,y=NULL
      )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      
      for (i in 1:length(covarList)){ # plot surface covars in this year
        
        plotDF$Covar = rollmean(data[[covarList[i]]][siteInd],k=k,fill=NA)
        
        plotList[[covarList[i]]] = ggplot(plotDF,aes(x=Date)
        )+geom_line(aes(y=Covar)
        )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
        )+coord_cartesian(xlim=c(st,ed)
        )+ggtitle(covarList[i]
        )+labs(x=NULL,y=NULL
        )+theme(plot.margin=margin(c(0,43,0,0),unit="pt"))
      }
      
      grid.arrange(grobs=plotList,ncol=1,nrow=length(covarList)+1,top=paste('Common Dolphins at',sites[j]))
      
    }
    
    
    for (i in 1:length(profileList)){ # for profiles of covars with multiple depth layers
      
      load(profileList[i])
      profileName = str_remove(str_remove(profileList[i],'_Profiles_ES.Rdata'),paste(profileDir,'/',sep=""))
      profileDF = data.frame(z=stack(data.frame(eval(parse(text=paste(sites[j],'Profile',sep="")))))[,1],
                             y=rep(depths,times=dim(eval(parse(text=paste(sites[j],'Profile',sep=""))))[2]),
                             x=rep(as.Date(masterData.Time,origin="1970-01-01"),each=length(depths)))
      
      for (m in 1:(length(dateMarks)-1)){
        st = dateMarks[m]
        ed = dateMarks[m+1]
        
        if (str_detect(profileName,"Asp")){
          
          plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
          )+geom_line(aes(y=Pres)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+coord_cartesian(xlim=c(st,ed)
          )+ggtitle('Presence'
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          direction_labeller <- function(x){
            ifelse(x %% 45 == 0, c('E','NE','N','NW','W','SW','S','SE')[1+(as.integer(x/45) %% 8)], '')}
          my_colors=c("#2E22EA","#9E3DFB","#F86BE2","#FCCE7B","#C4E416","#4BBA0F","#447D87","#2C24E9")
          
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+scale_fill_manual(
            values=my_colors,
            guide=NULL
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"))
          
          hues_df = data.frame(degree = 0:359) %>%
            mutate(
              label=direction_labeller(degree+90 %% 360),
              colors = colorRampPalette(my_colors)(360))
          
          plotList[["ColorLegend"]] = ggplot(hues_df
          )+geom_rect(aes(ymin=3,
                          ymax=4,
                          xmin=degree-0.5,
                          xmax=degree+0.5,
                          color=colors,
                          fill=colors)
          )+coord_polar(direction=-1,
                        start=0
          )+scale_color_identity(
          )+scale_fill_identity(
          )+guides(fill=FALSE,color=FALSE
          )+theme_void(
          )+ylim(c(1,4.5)
          )+geom_text(aes(x=degree,
                          y=4.5,
                          label=label)) 
          
          grid.arrange(plotList$Pres,plotList[[profileName]],plotList[["ColorLegend"]],
                       ncol=12,nrow=3,top=paste('Common Dolphins at',sites[j]),layout_matrix=rbind(c(rep(1,11),NA),
                                                                                                   c(rep(2,11),NA),
                                                                                                   c(rep(2,11),3)))
          
        } else {
          
          plotList[['Pres']] = ggplot(plotDF,aes(x=Date) # plot presence in this year
          )+geom_line(aes(y=Pres)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+coord_cartesian(xlim=c(st,ed)
          )+ggtitle('Presence'
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,40,0,0),unit="pt"))
          
          plotList[[profileName]] = ggplot(profileDF,aes(x=x,y=y,z=z) # plot profile for this year
          )+geom_contour_filled(
          )+coord_cartesian(xlim=c(st,ed)
          )+scale_x_continuous(breaks=c(seq.Date(from=st,to=ed,by="quarter"))
          )+scale_y_reverse(
          )+ggtitle(profileName
          )+labs(x=NULL,y=NULL
          )+theme(plot.margin=margin(c(0,0,0,0),unit="pt"),
                  legend.position="right",
                  legend.title=element_text(size=0),
                  legend.text=element_text(size=7),
                  legend.key.size=unit(0.5,'lines'),
                  legend.direction="vertical",
                  legend.margin=margin(0))
          
          
          grid.arrange(plotList$Pres,plotList[[profileName]],
                       ncol=12,nrow=3,top=paste('Common Dolphins at',sites[j]),layout_matrix=rbind(c(rep(1,12)),
                                                                                                   c(rep(2,12)),
                                                                                                   c(rep(2,12))))
        }
      }
    }
  }
}


```
Covars to start in full model: SSH
Sal0
Chl0
Temp0
Sal200
GSLat
Slope
Aspect

# Plot scatterplots and histograms
```{r plotCovars}
# Fill in smoothVarList based on selection made above
smoothVarList = c("SSH0",
                  "Chl0",
                  "Sal0",
                  "Temp0",
                  "Sal200",
                  "FSLE0",
                  "GSLat",
                  "Slope",
                  "Aspect")

pres = which(data$Pres>0)
presDF = data[pres,]
sites = c("HZ","BC","WC","BS")

for (i in 1:length(smoothVarList)){
  
  # Bootstrap the covar to produce a sample of the same size as pres
  refDist = sample(data[[smoothVarList[i]]],size=length(pres),replace=TRUE)
  
  # Compare empirical cumulative distribution functions with a Kolomogorov Smirnov test
  KS.out = ks.test(presDF[[smoothVarList[i]]],refDist,simulate.p.value=TRUE)
  
  # Plot presence bins across all data versus this covar
  edges = seq(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]),length.out=50)
  binDiff = diff(edges[1:2])
  plotDF = data.frame(Obs=histc(refDist,edges=edges)$cnt/length(refDist),
                      Pres=histc(presDF[[smoothVarList[i]]],edges=edges)$cnt/dim(presDF)[1],
                      BinCenter=seq(min(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    max(data[[smoothVarList[i]]])+(0.5*binDiff),
                                    by=binDiff))
  
  print(ggplot(plotDF
  )+geom_col(aes(x=BinCenter,y=Obs),
             fill='#bfbfbf',
             alpha=0.6
  )+geom_col(aes(x=BinCenter,y=Pres),
             fill='#66B2FF',
             alpha=0.5
  ) + labs(y="Normalized Counts",
           x=NULL,
           title=paste(smoothVarList[i],', p = ',as.character(KS.out$p.value),sep="")
  ) + theme_minimal())
  
  # print(ggplot(data
  # )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
  # )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
  #               method="loess"
  # )+labs(title=smoothVarList[i]))
  
  # Plot presence bins at each site versus this covar
  if (!str_detect(smoothVarList[i],"Slope") & !str_detect(smoothVarList[i],"Aspect")){
    for (j in 1:length(sites)){
      siteInd = which(!is.na(str_match(data$Site,sites[j])))
      if (length(siteInd)>7){
        print(ggplot(data[siteInd,]
        )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
        )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
                      method="loess"
        )+labs(title=paste(smoothVarList[i],'at',sites[j])))
      }
    }
  }
}


```

Starting covar list: "SSH0",
                    "Chl0",
                    "Sal0",
                    "Sal200",
                    "Temp0",
                    "Sal200",
                    "FSLE0",
                    "Slope",
                    "Aspect"

# Test for how a term should be included in the model
```{r smooth vs linear}

# Test whether continuous covars should be included in model as linear or smooth terms

startTime = Sys.time()
smoothVarList = c("SSH0",
                    "Chl0",
                    "Sal0",
                    "Sal200",
                    "Temp0",
                    "FSLE0",
                    "Slope",
                    "Aspect")

modOpts = c("linMod","threeKnots","fourKnots","fiveKnots")
QIC_votes = matrix(nrow=length(smoothVarList),ncol=5)

for (i in 1:(length(smoothVarList)-2)){

  
  # modelCall = paste('gam(Pres~data$',smoothVarList[i],',data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~data$',smoothVarList[i],',data=data,family=poisson,id=GroupID,corstr="ar1")',sep="")
  linMod = eval(parse(text=modelCall))
  
  # modelCall = paste('gam(Pres~s(data$',smoothVarList[i],',bs="cr"),data=data,family=poisson)',sep="")
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.5)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod1 = eval(parse(text=modelCall))
  
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.333,0.666)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod2 = eval(parse(text=modelCall))
  
  modelCall = paste('geeglm(Pres~mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275,0.5,0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],'))),data=data,family=poisson,id=GroupID,corstr=\"ar1\")',sep="")
  smoothMod3 = eval(parse(text=modelCall))
  
  QIC_votes[i,1:4] = c(QIC(linMod)[[1]],QIC(smoothMod1)[[1]],QIC(smoothMod2)[[1]],QIC(smoothMod3)[[1]])
  QIC_votes[i,5] = modOpts[which.min(QIC_votes[i,1:4])]
}

endTime = Sys.time()
endTime-startTime
colnames(QIC_votes) = c(modOpts,"Best")
rownames(QIC_votes) = smoothVarList[]
QIC_votes
```
Can't run Temp0 w 3 knots, Slope w 4 0r 5 knots, Aspect w 4 knots, gets stuck thinking forever

          linMod                 threeKnots          fourKnots           fiveKnots           Best        
SSH0   "-2477141.2406063"     "-2440898.49530487" "-2440835.85233785" "-2438947.71901698" "linMod"    
Chl0   "-2414078.06243844"    "-2444164.2080204"  "-2438509.39772769" "-2438997.46004147" "threeKnots"
Sal0   "-2383237.36057946"    "-2390841.29103607" "-2390286.3433856"  "-2390859.41657611" "threeKnots"
Sal200 "-2361449.26094234"    "-2363841.01791452" "-2362944.89524768" "-2362253.95247908" "threeKnots"
Temp0  "-2447760.39906554"    NA                  "-2472530.99153082" "-2471174.09405343" "linMod"    
FSLE0  "62377407.998108"      "-2384863.30521849" "-2384925.21901453" "-2384923.77081319" "threeKnots"
Slope  "9.08718799323797e+40" "-2523382.79180884" NA                  NA                  "threeKnots"
Aspect "-2354624.21837439"    "-2364930.87880944" NA                  NA                  "threeKnots"


# Make smooth terms, run full model and check collinearity
```{r fullModel}

smoothVarList = c("Chl0",
                  "Sal0",
                  "Sal200",
                  "FSLE0",
                "Slope",
                "Aspect")

linVarList = c("SSH0",
                "Temp0")
knotList = list(c(0.5),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.275,0.5,0.725))
smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  if (str_detect(smoothVarList[i],"Asp")){
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')),periodic=TRUE)',sep="")))
  } else {
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  }
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))

fullMod = geeglm(thisForm,
                family=poisson,
                data=data,
                id=GroupID,
                corstr="ar1")

VIFvals = vif(fullMod)
VIFvals = cbind(VIFvals,(VIFvals[,3])^2)
colnames(VIFvals)[4] = "LOOK AT ME"
VIFvals
# remove vars in stepwise fashion as necessary
```
            GVIF    Df  GVIF^(1/(2*Df)) LOOK AT ME
S_Chl0   15.978910  4        1.413980   1.999341
S_Sal0   24.454184  4        1.491228   2.223762
S_Sal200 16.281316  4        1.417298   2.008734
S_FSLE0  31.131057  4        1.536913   2.362101
S_Slope  22.773913  4        1.478018   2.184537
S_Aspect  9.261890  3        1.449161   2.100067
SSH0      2.403547  1        1.550338   2.403547
Temp0     3.067752  1        1.751500   3.067752

Everything looks good

# Check autocorrelation of residuals, revise grouping variable if necessary
```{r}
modACF = acf(residuals(fullMod),lag.max=180)

```
Super autocorrelated!

But changing the grouping variable doesn't have any effect at all on the residual autocorrelation. Going with the most conservative grouping variable of 126 days.

#Check term significance
```{r fullMod}

# Get p-values
getPvalues(fullMod)


```
Variable    p-value
S_Chl0	    0.000186			
S_Sal0	    0.017239			
S_Sal200  	0.108506			
S_FSLE0	    0.309092			
S_Slope	    0.006488			
S_Aspect	  0.217576			
SSH0	      0.026874			
Temp0	      0.020466

Removing Sal200, FSLE0, and Aspect because not significant

#Remove non-significant terms, re-run model, check p-values
```{r fullMod}
smoothVarList = c("Chl0",
                  "Sal0",
                "Slope")

linVarList = c("SSH0",
                "Temp0")
knotList = list(c(0.5),
             c(0.5),
             c(0.5))
smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  if (str_detect(smoothVarList[i],"Asp")){
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')),periodic=TRUE)',sep="")))
  } else {
    eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVarList[i],',knots=quantile(data$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  }
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))

reducedMod = geeglm(thisForm,
                 family=poisson,
                 data=data,
                 id=GroupID,
                 corstr="ar1")

# Get p-values
# getPvalues(reducedMod)


```
Variable    p-value
S_Chl0    	0.000131			
S_Sal0    	0.009037			
S_Slope	    0.00045			
SSH0	      0.026629			
Temp0	      0.020526

# Plot terms from regional model
```{r plot regional}

source("plotSmooths.R")
source("plotLinears.R")
terms = names(reducedMod$model)[2:length(names(reducedMod$model))]
k=3

for (i in 1:length(terms)){
  if (str_detect(terms[i],"S_")){ # plot smooth terms
    term = str_remove(terms[i],"S_")
  coefInd = which(str_detect(names(reducedMod$coefficients),term))
  if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
  print(plotSmooths(reducedMod,term,coefInd,k,periodic,site=NA,title=NULL))
  } else { # plot linear terms
    term=terms[i]
  coefInd = which(str_detect(names(reducedMod$coefficients),term))
  print(plotLinears(reducedMod,term,coefInd,site=NA,title=NULL))
  }
}

```

# Create site-specific models
# Don't include slope or aspect because they're only a single value for each site
```{r site-specific models}

sites = c("HZ","OC","NC","BC","WC","NFC","HAT","GS","BP","BS")
smoothVarList = c("Chl0",
                  "Sal0",
                  "Sal200",
                  "FSLE0")

linVarList = c("SSH0",
                "Temp0")
knotList = list(c(0.5),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.5),
             c(0.275,0.5,0.725))
siteModList = list()
pValList = list()


for (j in 1:length(sites)){
  siteInd = which(!is.na(str_match(data$Site,sites[j])))
  modDF = data[siteInd,]
  
  smoothNameList = character()
  
  for (i in 1:length(smoothVarList)){
    
    if (str_detect(smoothVarList[i],"Asp")){
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')),periodic=TRUE)',sep="")))
    } else {
      eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(modDF$',smoothVarList[i],',knots=quantile(modDF$',smoothVarList[i],',probs=unlist(knotList[i])),Boundary.knots=c(min(modDF$',smoothVarList[i],'),max(modDF$',smoothVarList[i],')))',sep="")))
    }
    
    smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
  }
  
  thisForm = formula(paste('Pres~',paste(c(smoothNameList,linVarList),collapse="+"),sep=""))
  
  siteModList[[sites[j]]] = geeglm(thisForm,
                                  family=poisson,
                                  data=modDF,
                                  id=GroupID,
                                  corstr="ar1")
  
  pValList[[sites[j]]] = getPvalues(siteModList[[sites[j]]])

}

print(pValList)

```
$HZ
  Variable  p-value
1   S_Chl0  0.02094
2   S_Sal0 0.192018
3 S_Sal200  <0.0001
4  S_FSLE0  <0.0001
5     SSH0 0.140846
6    Temp0 0.241479

$BC
  Variable  p-value
1   S_Chl0 0.000915
2   S_Sal0  <0.0001
3 S_Sal200  <0.0001
4  S_FSLE0 0.016447
5     SSH0 0.076101
6    Temp0  <0.0001

$WC
  Variable  p-value
1   S_Chl0  <0.0001
2   S_Sal0  <0.0001
3 S_Sal200  <0.0001
4  S_FSLE0 0.004491
5     SSH0 0.595285
6    Temp0  <0.0001

$BS
  Variable  p-value
1   S_Chl0  <0.0001
2   S_Sal0  0.08879
3 S_Sal200 0.002441
4  S_FSLE0 0.001336
5     SSH0 0.008824
6    Temp0  <0.0001


# Remove non-significant terms and rerun
```{r site-specific models}

siteModListRed = list()
pValListRed = list()
for (i in 1:length(siteModList)){
  site = names(siteModList)[i]
  badVars = pValList[[site]]$Variable[(pValList[[site]]$'p-value'>=0.05)]
    if (!isempty(badVars)){
  siteModListRed[[site]]<-eval(parse(text=paste("update(siteModList[[site]], . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
   pValListRed[[site]] = getPvalues(siteModListRed[[site]])
    } else {
      siteModListRed[[site]] = siteModList[[site]]
      pValListRed[[site]] = pValList[[site]]
    }
}

print(pValListRed)



```
$HZ
  Variable  p-value
1   S_Chl0  <0.0001
2 S_Sal200 0.393403
3  S_FSLE0  0.00125

$BC
  Variable  p-value
1   S_Chl0  <0.0001
2   S_Sal0 0.230803
3 S_Sal200 0.000241
4  S_FSLE0 0.002192
5    Temp0  <0.0001

$WC
  Variable  p-value
1   S_Chl0  <0.0001
2   S_Sal0 0.230803
3 S_Sal200 0.000241
4  S_FSLE0 0.002192
5    Temp0  <0.0001

$BS
  Variable  p-value
1   S_Chl0  <0.0001
2 S_Sal200 0.002245
3  S_FSLE0 0.002806
4     SSH0 0.007039
5    Temp0  <0.0001

# Again, remove non-significant terms and rerun
```{r site-specific models}


for (i in 1:length(siteModListRed)){
  site = names(siteModListRed)[i]
  badVars = pValListRed[[site]]$Variable[(pValListRed[[site]]$'p-value'>=0.05)]
  if (!isempty(badVars)){
  siteModListRed[[site]]<-eval(parse(text=paste("update(siteModListRed[[site]], . ~ . - ", paste(badVars,collapse="-"), ")", sep="")))
   pValListRed[[site]] = getPvalues(siteModListRed[[site]])
  }
}

print(pValListRed)



```
$HZ
  Variable p-value
1   S_Chl0 <0.0001
2  S_FSLE0 <0.0001

$BC
  Variable  p-value
1   S_Chl0  <0.0001
2 S_Sal200 0.000426
3  S_FSLE0 0.004257
4    Temp0  <0.0001

$WC
  Variable  p-value
1   S_Chl0  <0.0001
2 S_Sal200 0.000426
3  S_FSLE0 0.004257
4    Temp0  <0.0001

$BS
  Variable  p-value
1   S_Chl0  <0.0001
2 S_Sal200 0.002245
3  S_FSLE0 0.002806
4     SSH0 0.007039
5    Temp0  <0.0001

# Plot terms from site-specific models
```{r plot sites specific models}

source("plotSmooths.R")
source("plotLinears.R")

for (j in 1:length(siteModListRed)){
  
  terms = names(siteModListRed[[j]]$model)[2:length(names(siteModListRed[[j]]$model))]
  k=3
  siteName = names(siteModListRed)[j]
  
  for (i in 1:length(terms)){
    if (str_detect(terms[i],"S_")){ # plot smooth terms
      term = str_remove(terms[i],"S_")
      coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),term))
      if (str_detect(term,"Asp")){periodic=TRUE} else {periodic=FALSE}
      print(plotSmooths(siteModListRed[[j]],term,coefInd,k,periodic,site=siteName,title=siteName))
    } else { # plot linear terms
      term=terms[i]
      coefInd = which(str_detect(names(siteModListRed[[j]]$coefficients),term))
      print(plotLinears(siteModListRed[[j]],term,coefInd,site=siteName,title=siteName))
    }
  }
}

```






