---
title: "SpermWhaleModelSelection"
author: "RC + LB"
date: "4/22/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(geepack)
library(splines2)
library(lubridate)
library(tidyverse)
library(car)
library(splines2)
library(ggplot2)
source("getPvalues.R")

data = data.frame(read.csv('E:/ModelingCovarData/Master_DFs/SpermWhale_masterDF.csv'))
lagID = 126
numClust = length(data$Pres)/(lagID-1)
if (numClust<length(data$Pres)){
  clustID = rep(1:ceiling(numClust),each=lagID)
  clustID = clustID[1:length(data$Pres)]
} else {
  clustID = 1:length(data$Pres)
}
data$GroupID = clustID

# Round presence to get Poisson dist
data$Pres = round(data$Pres)
```

```{r temp0Lags}
# Test surface temperature at several time lags
var = "Temp0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names

AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp100Lags}
# Test temperature at 100m at several time lags
var = "Temp100"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp200Lags}
# Test temperature at 200m at several time lags
var = "Temp200"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp300Lags}
# Test temperature at 300m at several time lags
var = "Temp300"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp400Lags}
# Test temperature at 400m at several time lags
var = "Temp400"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp500Lags}
# Test temperature at 500m at several time lags
var = "Temp500"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp600Lags}
# Test temperature at 600m at several time lags
var = "Temp600"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r temp700Lags}
# Test temperature at 700m at several time lags
var = "Temp700"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal0Lags}
# Test salinity at 0m at several time lags
var = "Sal0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal100Lags}
# Test salinity at 100m at several time lags
var = "Sal100"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal200Lags}
# Test salinity at 200m at several time lags
var = "Sal200"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal300Lags}
# Test salinity at 300m at several time lags
var = "Sal300"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal400Lags}
# Test salinity at 400m at several time lags
var = "Sal400"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal500Lags}
# Test salinity at 500m at several time lags
var = "Sal500"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal600Lags}
# Test salinity at 600m at several time lags
var = "Sal600"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Sal700Lags}
# Test salinity at 700m at several time lags
var = "Sal700"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag0Lags}
# Test velocity magnitude at 0m at several time lags
var = "VelMag0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag100Lags}
# Test velocity magnitude at 100m at several time lags
var = "VelMag100"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag200Lags}
# Test velocity magnitude at 200m at several time lags
var = "VelMag200"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag300Lags}
# Test velocity magnitude at 300m at several time lags
var = "VelMag300"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag400Lags}
# Test velocity magnitude at 400m at several time lags
var = "VelMag400"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag500Lags}
# Test velocity magnitude at 500m at several time lags
var = "VelMag500"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag600Lags}
# Test velocity magnitude at 600m at several time lags
var = "VelMag600"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelMag700Lags}
# Test velocity magnitude at 700m at several time lags
var = "VelMag700"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp0Lags}
# Test velocity aspect at 0m at several time lags
var = "VelAsp0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp100Lags}
# Test velocity aspect at 100m at several time lags
var = "VelAsp100"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp200Lags}
# Test velocity aspect at 200m at several time lags
var = "VelAsp200"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp300Lags}
# Test velocity aspect at 300m at several time lags
var = "VelAsp300"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp400Lags}
# Test velocity aspect at 400m at several time lags
var = "VelAsp400"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp500Lags}
# Test velocity aspect at 500m at several time lags
var = "VelAsp500"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp600Lags}
# Test velocity aspect at 600m at several time lags
var = "VelAsp600"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r VelAsp700Lags}
# Test velocity aspect at 700m at several time lags
var = "VelAsp700"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r SSH0Lags}
# Test SSH at 0m at several time lags
var = "SSH0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r Chl0Lags}
# Test Chl at 0m at several time lags
var = "Chl0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r FSLE0Lags}
# Test FSLE at 0m at several time lags
var = "FSLE0"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```
```{r GSLatLags}
# Test GSLat at several time lags
var = "GSLat"
colInd = which(!is.na(str_match(colnames(data),var)))
AIC_comp = matrix(ncol=length(colInd),nrow=1)
names = character()

for (i in 1:length(colInd)){
mod = glm(Pres~mSpline(data[,colInd[i]],knots=quantile(data[,colInd[i]],probs=c(0.275,0.5,0.725)),
                           Boundary.knots=c(min(data[,colInd[i]]),max(data[,colInd[i]]))),
              data=data,family=poisson)
AIC_comp[1,i] = AIC(mod)[[1]]
names = c(names,colnames(data)[colInd[i]])
}

colnames(AIC_comp) = names
AIC_comp
colnames(AIC_comp)[order(AIC_comp)]
```

Covar selection to start: Temp0Lag56
                          Temp700Lag28
                          Sal0
                          Sal700Lag28
                          VelMag0 
                          VelMag700Lag7
                          VelAsp0Lag56 
                          VelAsp700Lag28
                          SSH0Lag14
                          Chl0Lag7
                          FSLE0
                          GSLatLag42
                          GSDist
                          Slope
                          Aspect
                          VelAsp700Lag28:Aspect


```{r plotCovars}
# Fill in smoothVarList based on selection made above
smoothVarList = c("Temp0Lag56",
             "Temp700Lag28",
             "Sal0",
             "Sal700Lag28",
             "VelMag0" ,
             "VelMag700Lag7",
             "VelAsp0Lag56" ,
             "VelAsp700Lag28",
             "SSH0Lag14",
             "Chl0Lag7",
             "FSLE0",
             "GSLatLag42",
             "GSDist",
             "Slope",
             "Aspect")

 pres = which(data$Pres>0)
  presDF = data[pres,]

 
for (i in 1:length(smoothVarList)){
  
   # Plot presence bins across all data for each covar
  edges = seq(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]),length.out=50)
  binDiff = diff(edges[1:2])
  plotDF = data.frame(Obs=histc(data[[smoothVarList[i]]],edges=edges)$cnt/dim(data)[1],
                    Pres=histc(presDF[[smoothVarList[i]]],edges=edges)$cnt/dim(presDF)[1],
                    BinCenter=seq(min(data[[smoothVarList[i]]])+(0.5*binDiff),
                                  max(data[[smoothVarList[i]]])+(0.5*binDiff),
                                  by=binDiff))

  print(ggplot(plotDF
  )+geom_col(aes(x=BinCenter,y=Obs),
             fill='#bfbfbf',
             alpha=0.6
  )+geom_col(aes(x=BinCenter,y=Pres),
             fill='#66B2FF',
             alpha=0.5
  ) + labs(y="Normalized Counts",x=NULL,title=smoothVarList[i]
  ) + theme_minimal())
  
  print(ggplot(data
  )+geom_point(aes(x=.data[[smoothVarList[i]]],y=Pres)
  )+geom_smooth(aes(x=.data[[smoothVarList[i]]],y=Pres),
                method="loess"
  )+labs(title=smoothVarList[i]))

}

```
Looks like there might be a trend: Temp0Lag56, VelAsp700Lag28?, SSH0Lag14?, GSDist?, Chl0Lag7

Looks like no trend: Sal0, Sal700Lag28, VelMag0, VelMag700Lag7, VelAsp0Lag56, FSLE0,
  GSLatLag42, Slope, Aspect

```{r checkVIF}
# calculate VIF for each of the variables desired in the full model
colMod = glm(Pres~
             +Temp0Lag56
             # +Temp700Lag28
             # +Sal0
             # +Sal700Lag28
             # +VelMag0
             # +VelMag700Lag7
             # +VelAsp0Lag56
             +VelAsp700Lag28
             # +SSH0Lag14
             +Chl0Lag7
             # +FSLE0
             # +GSLatLag42
             +GSDist,
             # +Slope
             # +Aspect,
             family=poisson,
             data=data)

VIFvals = vif(colMod)
VIFvals
# remove vars in stepwise fashion as necessary
```
Removing covars that have no apparent trend from plots above
Removing SSH because it is collinear with Temp700Lag28

```{r smooth vs linear}

# Test whether continuous covars should be included in model as linear or smooth terms

startTime = Sys.time()
smoothVarList = c("Temp0Lag42",
             "Temp700Lag7",
             "Sal0Lag21",
             "VelMag0Lag28" ,
             "VelMag700Lag7",
             "VelAsp0Lag14" ,
             "VelAsp700Lag28",
             "SSH0",
             "Chl0Lag7",
             "FSLE0",
             "GSLatLag14",
             "GSDist",
             "Slope",
             "Aspect")

termVote = matrix(ncol=length(smoothVarList),nrow=1)

for (i in 1:length(smoothVarList)){
  
  linMod = geeglm(Pres~data[[smoothVarList[i]]],data=data,family=poisson,id=GroupID,corstr="ar1")
  
   smoothMod = geeglm(Pres~mSpline(data[[smoothVarList[i]]],
                                   knots=quantile(data[[smoothVarList[i]]],probs=c(0.275,0.5,0.725)),
                                   Boundary.knots=c(min(data[[smoothVarList[i]]]),max(data[[smoothVarList[i]]]))),
                      data=data,
                      family=poisson,
                      id=GroupID,
                      corstr="ar1")
  
  QIC_vals = c(QIC(linMod)[[1]],QIC(smoothMod)[[1]])
  colnames(QIC_vals) = c("linMod","smoothMod")
  
  termVote[1,i] = colnames(QIC_vals)[which.min(QIC_vals)]
}

endTime = Sys.time()
endTime-startTime


```


```{r fullModel}
# Run full model and check autocorrelation of residuals, revise grouping variable if necessary

smoothVarList = c("Temp0Lag42",
             "Temp700Lag7",
             "Sal0Lag21",
             "VelMag0Lag28" ,
             "VelMag700Lag7",
             "VelAsp0Lag14" ,
             "VelAsp700Lag28",
             "SSH0",
             "Chl0Lag7",
             "FSLE0",
             "GSLatLag14",
             "GSDist",
             "Slope",
             "Aspect")

smoothNameList = character()

for (i in 1:length(smoothVarList)){
  
  eval(parse(text=paste('S_',smoothVarList[i],'= mSpline(data$',smoothVararList[i],',knots=quantile(data$',smoothVarList[i],',probs=c(0.275, 0.5, 0.725)),Boundary.knots=c(min(data$',smoothVarList[i],'),max(data$',smoothVarList[i],')))',sep="")))
  
  smoothNameList = c(smoothNameList,paste('S_',smoothVarList[i],sep=""))
}
 thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),sep=""))

colMod = geeglm(thisForm,
             family=poisson,
             data=data,
             id=GroupID,
            corstr="ar1")

modACF = acf(residuals(colMod),lag.max=180)

```


Changing the grouping variable doesn't have any effect at all on the residual autocorrelation, which is already quite minimal. Going with the most conservative grouping variable of 126 days.


```{r checkPV}
 #Add interaction term and run full model
thisForm = formula(paste('Pres~',paste(smoothNameList,collapse="+"),'+S_VelAsp700Lag28:Aspect',sep=""))

fullMod = geeglm(thisForm,
             family=poisson,
             data=data,
             id=GroupID,
            corstr="independence")

# Get p-values
getPvalues(fullMod)


```


